|

### 2023-09-08 chapter_4/src/prr/dcr_color_and_non-political_behaviors_prr.qmd
weak attempt to write

To test these hypotheses, I conduct an experiment involving a fictional real estate posting. The treatment involves randomly assigning participants to view one of two versions of a fictional real estate posting. The characteristics of the neighborhood are exactly the same between the two conditions except for the "favorite color of car" in the neighborhood. In the first condition the "favorite color of car" is reported by displaying a red swatch. In the second condition, the "favorite color of car" reported by displaying a blue swatch. Participants are then given a scale from 0-10 to rate the neighborhood and are presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?"

@@

Once the participants have responded to these questions, they are then given a "second page" describing the neighborhood. The information subjects sees depends on which of two conditions they are randomly assigned into. In one condition, the information indicates that the neighborhood is "40 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition presents the same information but instead describes the neighborhood as "10 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." With this new information, I ask participants "With this new information, please update your rating of the neighborhood" on the 0-10 scale and are again presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?"

@@

>>>>

To test these hypotheses, I conduct an experiment involving a fictional real estate posting. The treatment involves randomly assigning participants to view one of two versions of a fictional real estate posting. The characteristics of the neighborhood are exactly the same between the two conditions except for the "favorite color of car" in the neighborhood. In the first condition the "favorite color of car" is reported by displaying a red swatch. In the second condition, the "favorite color of car" reported by displaying a blue swatch. Participants are presented with a Likert scale to indicate, "How much would [they] like to live in this neighborhood?"

@@

Once the participants have responded to these questions, they are then given a "second page" describing the neighborhood. The information subjects sees depends on which of two conditions they are randomly assigned into. In one condition, the information indicates that the neighborhood is "40 minutes from the nearest metro area" and "60% voted for the Republican candidate in the latest congressional election." The second condition presents the same information but instead describes the neighborhood as "10 minutes from the nearest metro area" and "60% voted for the Democratic candidate in the latest congressional election." With this new information, I ask participants "How much would [they] like to live in this neighborhood?" and are given a 5-item Likert scale to record their response.

@@

The outcome of interest is a 5-item Likert scale. So the following models will be ordered logistic regressions. $H_1$ and $H_2$ would expect that when viewing the first page of the real estate flyer that Democratic participants would report a higher desire to move to a neighborhood with a blue swatch as opposed to a red swatch; the inverse would be true for Republican participants.
